Topological Classification of SCOPe

### 2019-04-22 paper/paper.tex
Add files via upload

\subsubsection{Small Dataset SCOPe1.55}

@@

\subsubsection{Large Dataset SCOPe2.07}

@@

%----------------------
\subsection{Convolutional Network Model}
%----------------------

@@

\subsubsection{ Mathematical Background}

\subsubsection{Persistence Homology}
As a visualization, we run the TDA on 2b7h, a protein of length ~120. We see that the barcodes do represent significant features of the protein such as alpha helices and beta sheets.

\begin{figure}[t]
	\includegraphics[width=\linewidth]{helixsimplex.png}
	\caption{TDA 2b7h detecting alpha helices }
	\label{fig:tdahelix}
\end{figure}

\begin{figure}[t]
	\includegraphics[width=\linewidth]{betasimplex.png}
	\caption{TDA 2b7h detecting beta sheets }
	\label{fig:tdabeta}
\end{figure}

\begin{figure}
	\includegraphics[width=\linewidth]{persistenceimages.png}
	\caption{Persistence Images}
	\label{fig:boat1}
\end{figure}
\subsubsection{ Sparse Persistence Homology}
\subsubsection{ Backbone Aware Persistence Homology}
\subsubsection{ Persistence Images}
We format the barcode data into three separate input features: persistent images, simplex distance map, and simplex grouping
\\
\textbf{Persistent Images:} The barcodes for each simplex are mapped into a 2-dimensional vector space with the first coordinate being the birth and the second coordinate being the persistence of the simplex. The plot cropped and converted to a blurred image at a set resolution. The range of the first and second coordinates to crop the plot were derived from the distribution of the data.

\begin{figure}
	\includegraphics[width=\linewidth]{xhist.png}
	\caption{x range}
	\label{fig:boat1}
\end{figure}

\begin{figure}
	\includegraphics[width=\linewidth]{yhist.png}
	\caption{y range}
	\label{fig:boat1}
\end{figure}

@@

%-------------------------------
%	BIBLIOGRAPHY
%---------------------------------
\pagebreak

\begin{thebibliography}{9}

>>>>

\subsubsection{Small Dataset SCOP 1.55}

@@

\subsubsection{Large Dataset SCOPe 2.07}

@@

%----------------------
\subsubsection{Convolutional Network Model}
%----------------------

@@

\subsubsection{ Mathematical Background}
\begin{defn}
K-Simplex is the convex hull of the standard basis of $ \mathbb{R}^{k+1} $
\end{defn}

\begin{defn}
Let $\sigma$ be a K-Simplex.
The vertex of $\sigma$ is the points.
The face of $\sigma$ are the simplices formed by subset of the vertices of $\sigma$.
2-face is a face of $\sigma$ with $2+1$ vertices.
\end{defn}

\begin{defn}
Simplicial complex is a topological space composed of set of simplices, $ \sum $, such that 
- Any face of a simplex $\sigma \in \sum$ is in $\sum$.
- The intersection of any two simplices in $ \sum $ is in $ \sum $
\end{defn}

\subsubsection{Persistence Homology}
We inspect the persistence homology of our protein '1ux8'. It is a protein of length 118.
Here is our protein chain. At each point, we search the radius around the point to find nearby points.

\begin{figure}[t]
	\includegraphics[width=\linewidth]{img/hom/ballRad1.png}
	\caption{TDA 2b7h detecting alpha helices }
	\label{fig:tdahelix}
\end{figure}
The red edges indicate that the two points are less than 3.5 distance away. Making them connected.
As we increase the radius, we connect more and more points.
\begin{figure}[t]
	\includegraphics[width=\linewidth]{img/hom/ballRad2.png}
	\caption{TDA 2b7h detecting alpha helices }
	\label{fig:tdahelix}
\end{figure}

The connections between these points form polygons (simplexes).
\begin{figure}[t]
	\includegraphics[width=\linewidth]{img/hom/ballRad3.png}
	\caption{TDA 2b7h detecting alpha helices }
	\label{fig:tdahelix}
\end{figure}
After a certain point we want to cut off our search radius because we have extracted all the notable features from our structure.
(If we keep increasing the search radius then all the points will be connected to each other)

A polygon is filled in when the inner polygons of the larger polygons are filled in.
We note that triangles are filled as soon as they are formed but larger structures take more time to get filled in.
Persistent homology tells us when (the radius) at which these polygons are created and filled in.

Below we have two examples of the polygons.
\begin{figure}[t]
	\includegraphics[width=\linewidth]{img/hom/Simplex1.png}
	\caption{TDA 2b7h detecting alpha helices }
	\label{fig:tdahelix}
\end{figure}

\begin{figure}[t]
	\includegraphics[width=\linewidth]{img/hom/Simplex2.png}
	\caption{TDA 2b7h detecting alpha helices }
	\label{fig:tdahelix}
\end{figure}

\begin{figure}[t]
	\includegraphics[width=\linewidth]{persistenceimages.png}
	\caption{Persistence Images}
	\label{fig:boat1}
\end{figure}
\subsubsection{ Sparse Persistence Homology}
\subsubsection{ Backbone Aware Persistence Homology}
\subsubsection{ Persistence Images}
We format the barcode data into three separate input features: persistent images, simplex distance map, and simplex grouping
\\
\textbf{Persistent Images:} The barcodes for each simplex are mapped into a 2-dimensional vector space with the first coordinate being the birth and the second coordinate being the persistence of the simplex. The plot cropped and converted to a blurred image at a set resolution. The range of the first and second coordinates to crop the plot were derived from the distribution of the data.

\begin{figure}[t]
	\includegraphics[width=\linewidth]{xhist.png}
	\caption{x range}
	\label{fig:boat1}
\end{figure}

\begin{figure}[t]
	\includegraphics[width=\linewidth]{yhist.png}
	\caption{y range}
	\label{fig:boat1}
\end{figure}

@@

%-------------------------------
%	BIBLIOGRAPHY
%---------------------------------
\pagebreak
\section*{Test}
\begin{thebibliography}{9}
